Model for DES Type Ia Supernova Cosmology Analysis

### 2016-05-08 tex/toy.tex
slight modification of toy model

For Case Not Typed the likelihood is
\begin{align}
\mathcal{L}(z_o,c_o | S_c, S_T, z, X) & =  \int dL \sum_i p(z_o,c_o | T_i, L, S_c, S_T, z, X) p(L |  T_i,  S_c, S_T, z, X) P(T_i|S_c, S_T, z, X).
\end{align}

For the redshift measurement, we take a set of potential host galaxies, where galaxy $j$
are redshift $z_j$ has probability $p_j$ of being the host
\begin{equation}
p(z_o|S_c, S_T, z, X) = \sum_j   p_j\delta(z_j-z).
\end{equation}
Then
\begin{align}
\mathcal{L}(z_o,c_o | S_c, S_T, z, X) & =  \sum_j p_j \int dL \,\sum_{i} p(c_o | T_i, L, S_c, S_T, z=z_j, X) p(L |  T_i,  S_c, S_T,  z=z_j, X) P(T_i|S_c, S_T, z=z_j, X) \\
&=  \frac{\sum_j p_j \int dL \, p(c_o, S_c, S_T | L, z=z_j, X) \sum_{i}  p(L|T_i, z=z_j, X) P(T_i|z=z_j, X)   }{P(S_c, S_T| z=z_j, X)}\\
&=  \frac{\sum_j p_j \int dL \, p(c_o | L, z=z_j, X) \sum_{i}  p(L|T_i, z=z_j, X) P(T_i|z=z_j, X)   }{P(S_c, S_T| z=z_j, X)},
\end{align}
where we use the fact that the counts do not directly depend on type.

>>>>

For Case Not Typed the likelihood is
\begin{align}
\mathcal{L}(z_o,c_o | S_c, S_T, z, X) & =  \int ds \,\mathcal{L}(z_o,c_o, s | S_c, S_T, z, X) \\
& =  \int ds \, \int dL \, \sum_i p(z_o,c_o, s | T_i, L, S_c, S_T, z, X) p(L |  T_i,  S_c, S_T, z, X) P(T_i|S_c, S_T, z, X).
\end{align}

For the redshift measurement, we take a set of potential host galaxies, where galaxy $j$
are redshift $z_j$ has probability $p_j$ of being the host
\begin{equation}
p(z_o|S_c, S_T, z, X) = \sum_j   p_j\delta(z_j-z).
\end{equation}
Then
\begin{align}
\mathcal{L}(z_o,c_o | S_c, S_T, z, X) & =  \sum_j p_j \int ds \, \int dL \,\sum_{i} p(c_o | T_i, L, S_c, S_T, z=z_j, X) p(s | T_i, L, S_c, S_T, z=z_j, X) \\
& \times p(L |  T_i,  S_c, S_T,  z=z_j, X) P(T_i|S_c, S_T, z=z_j, X) \\
& \propto  \sum_j p_j \int ds \, \int dL \,\sum_{i} p(c_o, S_c, S_T | T_i, L, z=z_j, X) p(s, S_c, S_T | T_i, L, S_c, S_T, z=z_j, X) \\
& \times p(L,, S_c, S_T |  T_i,  S_c, S_T,  z=z_j, X) P(T_i|S_c, S_T, z=z_j, X) \\
&=  \frac{\sum_j p_j \int dL \, p(c_o, S_c, S_T | L, z=z_j, X) \sum_{i}  p(L|T_i, z=z_j, X) P(T_i|z=z_j, X)   }{P(S_c, S_T| z=z_j, X)}\\
&=  \frac{\sum_j p_j \int dL \, p(c_o | L, z=z_j, X) \sum_{i}  p(L|T_i, z=z_j, X) P(T_i|z=z_j, X)   }{P(S_c, S_T| z=z_j, X)},
\end{align}
where we use the fact that the counts do not directly depend on type.
